Forecasting the power of Higher Order Weak Lensing Statistics with automatically differentiable simulations

### 2023-03-16 paper/authors.tex
Added a new section
revisited after 1 review

% paper leads
\author{Denize Lanzieri}
\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}

\author[0000-0001-7956-0542]{Fran\c{c}ois Lanusse}
\affiliation{AIM, CEA, CNRS, Universit\'e Paris-Saclay, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, F-91191 Gif-sur-Yvette, France}

%main partticipants and text contributors  (alphabetical)
\author{Chirag Modi}
\noaffiliation

% minor contributions and/or text writers (alphabetical)

>>>>

% paper leads
\author{Denise Lanzieri}
\affiliation{Université Paris Cité, Université Paris-Saclay, CEA, CNRS, AIM, F-91191, Gif-sur-Yvette, France}

\author[0000-0001-7956-0542]{Fran\c{c}ois Lanusse}
\affiliation{Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France; }

%First Tier authors (alphabetical)
\author{Chirag Modi}
\affiliation{Center for Computational Astrophysics,
Center for Computational Mathematics,
Flatiron Institute, New York, NY 10010, USA}
% \noaffiliation

\author{Benjamin Horowitz}
\affiliation{Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, 94720, CA, USA}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

\author{Joachim Harnois-Déraps}
\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Herschel Building, NE1 7RU Newcastle-upon-Tyne, UK}
% Second Tier authors (alphabetical)
\author{Jean-Luc Starck}
\affiliation{Université Paris-Saclay, Université Paris Cité, CEA, CNRS, AIM, 91191, Gif-sur-Yvette, France; }
